\documentclass{article}

\usepackage{xcolor}
\usepackage{calc}
\usepackage{hyperref}
\usepackage[a4paper]{geometry}
\usepackage[parfill]{parskip}
\usepackage{amsmath}
\usepackage{graphicx}

\title{{Snowmelt Cup II}\\{\Huge Invitational Tournament Rules}}
\date{}

\newcommand{\scoreformula}[1]{{\color{red} #1}}
\newcommand{\notestyle}[1]{\textsc{\lowercase {#1}}}
\newcommand\Points{\text{Points}}
\newcommand\MaxPure{\notestyle{Max Pure}}
\newcommand\Pure{\notestyle{Pure}}
\newcommand\Far{\notestyle{Far}}
\newcommand\Lost{\notestyle{Lost}}
\newcommand{\coloneq}{\mathrel{\resizebox{\widthof{$\mathord{=}$}}{\height}{ $\!\!\resizebox{1.2\width}{0.8\height}{\raisebox{0.23ex}{$\mathop{:}$}}\!\!=\!\!$ }}}

\begin{document}

\maketitle
\pagenumbering{gobble}
\frenchspacing

\section{Arrangements}

A total of 9 players will be randomly divided into teams of 3.
In each round of the music play, any 2 players from the same team will participate.
Each player is permitted to perform a maximum of 5 times.


\section{Song Pool}

The song pool will include all songs
(up until the latest Arcaea update)
with difficulty ranging 10.4--12.0.


\section{Song Selection \& Ban/Pick}

Every team will choose to ban 1 song AND pick 2 songs. The referee will then
randomly select an additional song, resulting in a total of 7.
Banned songs will be revealed 1 hour prior to the match.


\section{Schedule}

The event is scheduled to take place from 28/8 to 30/8, with the
specific timing to be determined by the players.

Following the announcement of each song, every team will be designated
periods for discussion (3 minutes), music play (6 minutes) and moment of
respite (3 minutes).


\section{Special Rule: Pick Reveal}

Each team will decide to disclose one of their picks and
indicate whether it's the one with a higher or lower difficulty
(or either in case of having the same difficulty).
The outcomes will be unveiled 30 minutes before the match.


\section{Other Details}

\begin{itemize}

	\item Handcams are required for the entire event.
	      Players who decide to livestream the gameplay
	      should prepare a clear recording.

	\item Prior to the starting of each round,
	      provide your team's selection of candidates
	      to the referee during the discussion phase.
	      This choice may not be changed once the play starts.

	\item Following each play, promptly capture a \textbf{timestamped} screenshot
	      of the play results, displaying the breakdown of your \Pure{} counts, then
	      submit to the referee without delay. Additionally, you will need to
	      submit your handcam at the end of the match.

\end{itemize}

\section{Scoring}

Formula:

\scoreformula{
	\begin{align*}
		\Points        & \coloneq \frac{M + 0.9P + 0.2F}{N} \\
		\text{where}~M & = \text{No.~of \MaxPure,}          \\
		P              & = \text{No.~of \Pure,}             \\
		F              & = \text{No.~of \Far,}              \\
		N              & = \text{Total count of notes}
	\end{align*}
}

\end{document}
