\documentclass{article}

\usepackage{xcolor}
\usepackage{amsmath}
\usepackage[a4paper]{geometry}
\usepackage[parfill]{parskip}
\usepackage[noabbrev,nameinlink,capitalise]{cleveref}
\usepackage{siunitx}
\usepackage{microtype}

\title{{Snowmelt Cup II}\\{\Huge Rules}}
\author{}
\date{}

\newcommand{\alert}[1]{{\color{red} #1}}
\newcommand{\penalyformula}[1]{{\color{cyan} #1}}
\newcommand{\startsectionfromzero}{\setcounter{section}{-1}}
\newcommand{\srbgcolor}{red!40}
\newcommand{\specialrule}[1]{\hfuzz=100pt  % overfull hbox doesn't matter here
	\colorbox{\srbgcolor}{\parbox{\textwidth}{#1}}}
\newcommand{\beyond}{\textsf{Beyond}}

\startsectionfromzero
\frenchspacing
\renewcommand\arraystretch{1.3}

\begin{document}
\maketitle
\alert{
	Any personnels closely related to the tournament,
	including while not limited to
	the participants and the judges,
	are strictly prohibited from
	proceeding with any form of
	violations against the fairness of the event,
	nor any form of activities aiming to
	harm the others' legitimate interests.
	Violators may face penalties
	and take personal responsibility for the consequences.
}

\section{Application requirements} \label{sec:application-requirements}

Contestants are required to:

\begin{enumerate}
	\item Be able to record clear handcams.
	\item Be possessing $\geq \qty{80}{\percent}$ of the charts
	      in their own division (see \cref{subsect:divisions}),
	      including all with chart constant $\geq 10$
	      except for those of \beyond{} difficulty
	      AND being included in a song pack other than
	      Main Story chapters.
	      \begin{itemize}
		      \item If this has become an issue,
		            please inform FLAME, the host of event in advance.
	      \end{itemize}
\end{enumerate}

\section{Number of contestants: 48}

\section{Formal rules}

\subsection{Divisions}\label{subsect:divisions}

Throughout the tournament,
contestants will be split into 3 divisions:
Speed~(S), Technical~(T) and Complicated~Beats~(Cb).
Songs will be classified
into 3 categories correspondingly,
namely class songs.

\begin{table}[!htbp]
	\centering
	\begin{tabular}{cl}
		\hline
		Category & What to expect                                                                \\ \hline
		S        & Charts testing the ability to cope with high-speed note patterns              \\
		T        & Charts testing positioning and the ability to cope with complex note patterns \\
		Cb       & Charts testing the ability to cope with complex rhythm                        \\ \hline
	\end{tabular}
\end{table}

\alert{
	The specific allocation of the songs  % <!-- or 'charts'? -->
	will be revealed by the time of application.
}

Contestants will only compete with each other
within their own division,
using and ban/pick'ing songs of their own category.
Part of the songs may be classified into multiple categories.

\subsection{Audition}

Contestants may freely choose their desired division
during application,
by which 3 class songs for each category will be published.
Once decided, the contestants will need to play through the chosen class songs in a stretch,
and submit the handcam and the screenshots of all 3 play results.
Retrying, re-recording and editing the handcam will be forbidden.  % <!-- should we emphasise that pausing is allowed ? -->
One may also switch to another division before the deadline.
If so, the contestant should inform one of the staff about the change,
and go through the same procedure once more as above,
using the new choice of songs.  % <!-- verbose -->

At the end of the audition,
contestants will be ranked
according to their scores on the class songs.
\textbf{In case of division A having $\mathbf{> 16}$ contestants
	AND B with $\mathbf{< 16}$,
	the prospective contestants eliminated from A
	will be given the opportunity to switch to B,
	but with a ranking certainly lower than
	anyone else originally placed there.}
Contestants who decide to switch
will need to go through the same
audition procedure as aforementioned,
and those ranked lower than 16 still will be eliminated
once for all.  % bit of disrespectful?
(Note: to successfully switch, contestants
must possess the required songs
as stated in \cref{sec:application-requirements}.)

Otherwise if all the divisions have had $\geq 16$ contestants,
those ranked lower than 16 will be eliminated.
Contestants who passed will then be examined for
possessing the required songs.
Contestants also need to bind with Bot
using their Arcaea friend code.
Anyone not possessing the required songs
will be disqualified and being
replaced by a previously eliminated
contestant in the division,
in the order of ranking.

\subsection{Round I: Group Stage, 16 into 8}

Within the same division,
contestants will be arranged into \emph{groups} of 4.
Each group will be allocated with a judge,
who will randomly select \emph{6 non-repeating songs}
from the pool in the relevant category
for the upcoming matches.
Before the matches begins,
both competing contestants
may DM the judge to pick one and only one song,
to increase its chance of being selected
in their participating round by \qty{25}{\percent},
AND/OR ban one and only one song.
When applied on the same song,
a pick and a ban cancel out each other.
The song picked/banned must be within
the pool of the corresponding division.
Contestants may not make changes to their choices later.

The final ranking of each member in the group will be determined
after all the matches in the group have finished.
Top 2 contestants will advance to the next round.

Grouping of contestants will be decided
by the rankings from the audition
(e.g. contestants ranked 1, 5, 9, 13
will be grouped together).

\alert{
	The songs with chart constant 9.3--10.9
	will be in the range of the selection for this round.
}

\subsection{Round II: Individual matches, 8 into 4}

Every victor  % not yet champion, i guess? 
from the last round
will be paired with a runner-up
from a different group for a match.

Procedure: Each contestant bans 3 songs $\rightarrow$
the judge announces the banned songs $\rightarrow$
each contestant picks 2 songs $+$ the judge picks 1 song by random $=$ 5 songs in total.
The contestant with the higher points advances to the next round.
(Ban/Pick must be done half an hour before the match)

\specialrule{
	Special rule: After finishing picking,
	a contestant may DM the judge with ``high'' or ``low''
	to take a sneak peek at
	the approximate chart constant of the opponent's pick
	($\pm0.1$).
}

\nopagebreak

\alert{
	The songs with chart constant 9.7--11.5
	will be in the range of the selection for this round.
}

\subsection{Round III: Comeback % <!-- expect better substitutes --> 
	matches \& Finals}

\paragraph{Comeback matches.}
4 eliminated contestants
from Round II will rematch to yield the top 2
(ranked 5th and 6th).

The procedure and \colorbox{\srbgcolor}{special rule}
will remain the same as in Round I
except without picking songs
and the number of songs reduces to 3.
The range of the songs stays the same as in Round II.

\paragraph{Finals.}
4 winning contestants from Round II
will be ranked from 1st to 4th place
according to their points.

Contestants placed 5th and 6th, the offensive,
will need to each challenge any
one of the top 4 contestants, the defensive.
The 5th place contestant will be prioritised to make the decision.

The finals will be divided into two parts in terms of procedure.

\paragraph{Part 1}

\begin{itemize}
	\item When either the 1st or 2nd place contestant has been challenged:
	      for a successful challenge, two contestants will swap places;
	      otherwise the challenger will be eliminated.

	\item When either the 3rd or 4th place contestant has been challenged:
	      in case of a successful challenge,
	      the challengee  % is there really such word? 
	      will be eliminated, with the challenger taking over  % expect better wording
	      their place;
	      otherwise the challenger will be eliminated.
\end{itemize}

\paragraph{Part 2}

\begin{itemize}
	\item If there are still 6 contestants left after Part 1,
	      then the 5th and 6th place contestants must each challenge
	      one of the 3rd or 4th place contestants,
	      following the same rules as Part 1.

	\item After challenges, the 3rd and 4th place contestants
	      must challenge one of the 1st or 2nd place contestants.
	      The winning contestants will enter the champion match,
	      and the losing contestants will contend for the
	      second and third runner-up.
	      The procedure and \colorbox{\srbgcolor}{special rule} of which
	      will remain the same as Round II,
	      except two more random songs will be added
	      to the pool in the champion match.
\end{itemize}

\alert{
	The songs with chart constant 10.5--12.0
	will be in the range of the selection for this round.
}

\section{Scoring}

\subsection{Definitions}
\emph{Score} refers to your in-game play result.
\emph{Point} refers to your score in the tournament,  % informal
derived from the play result
using a calculating procedure known as \emph{scoring}.

\newcommand{\Points}{\text{Points}}

\subsection{Single song scoring}
The points of a single music play are calculated as follows:
\alert{
	\begin{align*}
		\Points        & = \frac{M + 0.9P + 0.2F}{N}   \\
		\text{where}~M & = \text{No.~of Max Pure,}     \\
		P              & = \text{No.~of Pure,}         \\
		F              & = \text{No.~of Far,}          \\
		N              & = \text{Total count of notes}
	\end{align*}
}

\subsection{Bonus}

Conditions for bonus are division-dependent.
Once triggered, an alternative scoring formula
will be used instead.

\begin{itemize}
	\item Division S: require $(S_\text{me} - S_\text{opponent} \geq \num[group-separator={,}]{10000})$, where $S = \text{Score}$
	      \alert{
		      \begin{equation*}
			      \Points = \frac{M + 0.96P + 0.2F}N
		      \end{equation*}
	      }

	\item Division T: require $(L_\text{me} \leq L_\text{opponent})$, where $L = \text{No.~of Lost}$
	      \alert{
		      \begin{equation*}
			      \Points = \frac{M + 0.9P + 0.5F}N
		      \end{equation*}
	      }

	\item Division Cb: require $(P_\text{me} - P_\text{opponent} \geq 10$ \emph{AND} $S_\text{me} \geq \num[group-separator={,}]{9970000})$
	      \alert{
		      \begin{equation*}
			      \Points = \frac{M + 0.9P + 0.2F + 0.75L}N
		      \end{equation*}
	      }
\end{itemize}

\subsection{Overtime penalty}
\penalyformula{
	\begin{align*}
		\text{Penalty}(song) & = \Points(song) \times \left(1-\frac{{T}^2} {3600}\right) \\
		\text{where}~T       & = \text{Overtime in seconds}
	\end{align*}
}

\subsection{Audition scoring}

Audition points summarise the single song points
for all three class songs.

\section{Time allocation}

\begin{itemize}

	\item Upon confirming the grouping,
	      contestants should reach out to their opponents
	      in order to determine the schedule of matches
	      and duly notify the judge.

	\item Should a contestant wish to ban/pick a song,
	      they will need to notify the judge at least 30 minutes
	      prior to the commencement of the match.

	\item During the group stage (Round I),
	      every match will begin 1 minute
	      after the song being announced.
	      Contestants will be given 5 minutes for the music play,
	      during which they may restart if they wish.
	      Following that, a 4-minute moment of respite will be given
	      before the next match begins, if any remaining.

	\item While matches could be separately scheduled,  % how about "asynchronously"
	      contestants are recommended to finish up their matches
	      as sooner as possible,
	      for the convenience of statistics.  % <!-- feels weird man -->

	\item Individual matches (Round II) will be using the same time allocation as in Round I.
\end{itemize}

\section{Handcams \& screenshots}

\begin{itemize}
	\item Handcam will be required throughout the tournament;
	      the recording of which should remain unedited,
	      and include timestamps
	      at both the beginning and end of the music play,
	      accurate to the second,
	      based on Coordinated Universal Time (UTC).

	\item Contestants should always remember to capture
	      a timestamped screenshot of the play result
	      when finishing a music play.
	      Therefore, in case of a mistakenly ruled overtime,
	      the screenshot/handcam could be
	      submitted as evidence for the judges to review.

	\item Only the winning contestants need to submit the handcam
	      at the end of the match.

	\item Exception: one would \textbf{never}
	      trigger the overtime penalty
	      by retrying a song
	      for \textbf{no more than once},
	      regardless of whether the timeout occurs.
	      In case of a wrongful judgement,
	      please appeal to the staff team.
\end{itemize}

\section{Ban/Pick}

Unless otherwise stated, ban/pick are defined as follows:

\begin{itemize}
	\item Ban: to disable a song from appearing in the current round.

	\item Pick: to make a song definitely appearing in the current round.

	\item During the group stage (Round I),
	      banned and picked song will be revealed
	      at the end of the round.
	      \begin{itemize}
		      \item \alert{
			            Note: repeated picks on one
			            song will be considered as one pick only.
		            }
	      \end{itemize}

	\item During the individual matches (Round II),
	      the banned songs will be revealed before the commencement of each match,
	      from which contestants will not be able to pick.
	      Picked songs will be revealed at the end of the round.
	      \begin{itemize}
		      \item \alert{
			            Note: repeated picks on one
			            song will be considered as one pick only,
			            and a random song,
			            guaranteed not to be
			            overlapping with the pick songs,
			            will kick in.  % <!-- informal -->
		            }
	      \end{itemize}
\end{itemize}

\section{Schedule}

All the timestamps below are in form of
\texttt{yyyy/mm/dd} (\texttt{HH:MM}), GMT+8.

\begin{table}[!ht]
	\centering
	\begin{tabular}{lc}
		\hline
		Event     & Schedule                           \\ \hline
		Audition  & 2023/07/16 12:00--2023/07/30 00:00 \\
		Round I   & 2023/08/01--2023/08/10             \\
		Round II  & 2023/08/11--2023/08/18             \\
		Round III & 2023/08/19--2023/08/26             \\ \hline
	\end{tabular}
\end{table}

\section{Time slots}

All the timestamps below use the form of
\texttt{HH:MM}, GMT+8.

\begin{itemize}
	\item Round I/II: 8:00--9:00, 14:00--15:00, 15:30--16:30, 19:00--20:00, 20:30--21:30

	\item Round III will take the same time slots as Round II
	      but with an additional 20 minutes appended to each.

	\item Should you have any other time arrangements,
	      please contact the judge who will
	      try to accommodate as much as possible.

	\item Please bear in mind that
	      the time slots do not include the ban/pick stage,
	      which will be instead scheduled 30 minutes prior to the commencement.
\end{itemize}

\section{Prizes}

\begin{table}[!htbp]
	\centering
	\begin{tabular}{ll}
		\hline
		Achievement  % bad wording!
		                 & Prize                                    \\ \hline
		Champion         & Arcaea Sound Collection Album per person \\
		First runner-up  & 1000 Memories per person                 \\
		Second runner-up & 800 Memories per person                  \\
		4th--6th place   & 500 Memories per person                  \\
		7th--8th place   & 300 Memories per person                  \\
		9th--16th place  & 200 Memories to two by random            \\ \hline
	\end{tabular}
\end{table}

Each division would yield a set of the above standings,
i.e.,
three champions will be produced in total---%
one from each division---%
and so will the rest be determined.

All the prizes will be awarded in form of  % maybe 'be converted'? 
cash---every Arcaea Sound Collection Album converts to ¥150,
and every 100 Memories converts  % convert or converts??? 
to ¥6.

\end{document}
